\documentclass[titlepage,12pt]{book}
\usepackage[utf8]{inputenc}

\include{../preamble}

\begin{document}

\mainmatter

\begin{solution}
    Sequence $a_{1},a_{2},a_{3},a_{4},a_{5}$
    \enum {
        \item
            \begin{proof} 
                By Contradiction.
                Suppose that there is no 3-chain in our sequence and $a_{1} \leq a_{3}$.
                If $a_{4} \geq a_{3}$ then we have 3-chain with $a_{1}, a_{3}, a_{4}$.
                This implies $a_{4} < a_{3}$.
                
                If $a_{4} < a_{3}$ then $a_{1} < a_{2}$ and $a_{1} \leq a_{3}$ implies $a_{3} < a_{2}$.
                So, $a_{4} < a_{3} < a_{2}$ is a 3-chain.
                This implies $a_{4} \geq a_{3}$.
                Contradiction.

                Thus $a_{1} > a_{3}$.
            \end{proof}

        \item 
            \begin{proof}
                If there is no 3-chain then $a_{1} > a_{3}$.
                So, $a_{3} < a_{2}$. Now, $a_{4} >  a_{3}$ and $a_{4} < a_{2}$ for no 3-chain to exist.
                Thus, $a_{3} < a_{4} < a_{2}$.
            \end{proof}

        \item
            \begin{proof}
                We have $a_{1} < a_{2}$ and $a_{3} < a_{4} < a_{2}$.

                $a_{5} \geq a_{2}$ will result in 3-chain $a_{1}, a_{2}, a_{5}$
                $a_{5} \geq a_{4}$ will result in 3-chain $a_{3}, a_{4}, a_{5}$
                $a_{5} \geq a_{1}$ will result in 3-chain $a_{3}, a_{4}, a_{5}$ or $a_{2}, a_{4}, a_{5}$.
                $a_{5} \geq a_{3}$ will result in 3-chain $a_{2}, a_{4}, a_{5}$.
                $a_{5} \leq a_{3}$ will result in 3-chain $a_{2}, a_{3}, a_{5}$.

                Thus any value of $a_{5}$ produces a 3-chain.
            \end{proof}

        \item
            \begin{proof}
                By Contradiction.
                Suppose $\exists a_{1},a_{2},a_{3},a_{4},a_{5}$ such that no 3-chain exists.

                If $a_{1} > a_{2}$ then,
                $a_{2} < a_{3} < a_{1}$ then any $a_{4}$ will create 3-chain.

                $a_{2} < a_{1} < a_{4} < a_{3}$ any $a_{5}$ will create 3-chain.


                If $a_{1} < a_{2}$ then, $a_{1} > a_{3}$ and $a_{3} < a_{4} < a_{2}$.
                But now, any $a_{5}$ will create a 3-chain.

                Contradiction.
            \end{proof}
    }
\end{solution}

\begin{solution}
    By Induction.
    
    
    Induction Hypothesis: $P(n)$ implies for all non negative integer $n$, 
    
    $\sum_{i=0}^{n} i^{3} = ((n(n+1)) / 2)^{2}$

    
    Base case: $n = 0$. $P(0)$ is $\sum_{i=0}^{0} i^{3} = 0 = ((0(0+1)) / 2)^{2}$.
    Thus, $P(0)$ is true.

    For induction, assume $P(n)$ is true.
    Now, $P(n+1)$ is $\sum_{i=0}^{n+1} i^{3} = (((n + 1)(n+2)) / 2)^{2}$.

    Then, $\sum_{i=0}^{n+1} i^{3} = \sum_{i=0}^{n} i^{3} + (n + 1)^{3}$.

    $((n(n+1))/2)^{2} + (n + 1)^{3} = (n + 1)^{2}(n^{2}/4 + (n + 1)) = (n + 1)^{2}((n^{2}+ 4n + 4)/4) = (n + 1)^{2}((n+ 2)^{2}/4) = (((n + 1) (n + 2)) / 2)^{2}$.

    Therefore $P(n) \implies P(n+1)$.

    By the axiom of induction $P(n)$ is true.

\end{solution}


\begin{solution}
    By induction.
    
    Suppose that the num edges can reach beyond the grid.
    Then for any $m < n$, num edges is atmost $4m$ which is less than $4n$.
    And for full grid num edges is exactly $4n$.

    Let $x$ denote the num edges.

    States:
    If a new square is infected 
        it will cancel at least two edges and add at most two edges.
    After any legal move the state of the grid will change in following ways:

    \enumr {
        \item $x$ will remain unchanged.
        \item $x$ will decrease by 1.
        \item $x$ will decrease by 2.
        \item $x$ will decrease by 4.
    }

    Induction Hypothesis: $P(m)$ implies after $m$ time-steps, 
        $x < 4n$ for $n \times n$ grid.

    Base Case: $P(0)$ is true. Because, $m < n$ and $x \leq 4m < 4n$.

    Assume it is true for all $m$ for purposes of induction.

    After $m + 1$ steps the state changes. But the new state  $x'$
    will be $x' \leq x$. Since $x < 4n$ (from induction hypothesis).
    $x' < 4n$.

    It follows that $P(m) \implies P(m + 1)$.
    Thus $P(m)$ is true.
\end{solution}

\begin{solution}
    The inductive hypothesis only covers $a^{k}$ not $a^{-1}$.
    Assuming $a^{-1} = 1$ requires base case to consider $k = 1$.
    But the base case only considers $k = 0$.
    Simply assuming $a^{-1} = a^{1} = 1$ assumes $P(k + 1)$ is true implicitly.
    But the proposition $P(k + 1)$ is the thing we are trying to prove.
\end{solution}

\begin{solution}
    By Induction:
    $P(n)$ be $G_{n} = 3^{n} - 2^{n}$.

    Special Case: For $n = 0$. $G_{0} = 0$ which is true.

    Base Case: For $n = 1$. $G_{1} = 1$ which is true.

    Inductive Step: Assume $\forall n \geq 1, P(n)$ is true.

    $P(n + 1)$ is $G_{n + 1} = 3^{n+1} - 2^{n + 1}$.
    So, $G_{n + 1} = 5 G_{n} - 6 G_{n - 1} 
    = 5 (3^{n} - 2^{n}) - 6 (3^{n - 1} - 2^{n - 1})
    = 5 \cdot 3^{n} - 5 \cdot 2^{n} - 2 \cdot 3^{n} + 3 \cdot 2^{n}
    = 3 \cdot 3^{n} - 2 \cdot 2^{n}
    = 3^{n + 1} - 2^{n + 1}
    $

    which implies that $P(k + 1)$ holds.
    If follows by induction that $P(k)$ holds for all $k \in \mathbb{N}$.


\end{solution}



\begin{solution}
    \enum{
        \item No. A row move moves a tile from cell $i$ to either $i + 1$ or $i - 1$.
            Nothing else moves. 
            If you're going from $i$ to $i + 1$, 
            everything leq than $i - 1$ and geq than $i + 2$ stays the same 
            and relative order does not change.

            If you're going from $i$ to $i - 1$,
            everything leq than $i -2$ and geq than $i + 1$ stays the same
            and relative order does not change.

        \item A column move changes relative order of 2 pairs of letters.
        
        A column move moves a tile from cell $i$ to either $i + 3$ or $i - 3$.
        When an item moves 3 positions it changes order with 2 items $i + 1, i + 2$ or $i - 1, i - 2$.

        \item A row move does not change the relative order of items in the grid.
        Hence it does not affect the parity of the number of inversions.

        \item A column move changes the relative order of 2 pairs of letters.
        The number of inversions either stays the same 
        or increases by 2 or decreases by 2 during a column move.
        Adding/subtracting 2 does not change parity.
        Thus a column move doesn't change parity of inversions.

        \item In every state reachable from the given configuration of the grid
        the parity of number of inversions is odd.

        \item 
        \begin{lemm}[A row move does not change the relative ordering]
            A row move moves a tile from cell $i$ to either $i + 1$ or $i - 1$.
            Nothing else moves. 
            If you're going from $i$ to $i + 1$, 
            everything leq than $i - 1$ and geq than $i + 2$ stays the same 
            and relative order does not change.

            If you're going from $i$ to $i - 1$,
            everything leq than $i -2$ and geq than $i + 1$ stays the same
            and relative order does not change.
        \end{lemm}

        \begin{lemm}[A column move changes the relative ordering of 3 pairs of letters]
            A column move moves a tile from cell $i$ to either $i + 4$ or $i - 4$.
        When an item moves 4 positions it changes order with 3 items $i + 1, i + 2, i + 3$ or $i - 1, i - 2, i - 3$.
        \end{lemm}

        \begin{proof}
            By induction:
            $P(n)$ be the proposition that after $n$ steps the parity of
            the number of inversions is different from the parity of the
            row containing the blank sqaure.

            Base Case: $P(0)$ is true because parity of number of inversions (which is 1) is odd.
            The parity of row containing the blank square (which is 4) is even.

            Inductive Step: For the purposes of induction, assume $P(n)$ is true for all $n$.
            Consider a sequence of $n + 1$ moves, $m_{1}, m_{2}, \cdots m_{n + 1}$.

            Now by the inductive hypothesis, we know that
            after $m_{1} \cdots m_{n}$ is the parity of
            the number of inversions, $inv$ is different from the parity of the
            row containing the blank sqaure, $i$.

            % After $m_{1} \cdots m_{n}$ moves, the 

            % \enumr{
            %     \item blank sqaure in odd row and parity of number of inversions is even.
            %     \item blank sqaure in even row and parity of number of inversions is odd.
            % }
            On the $m_{n + 1}$ move,
            
            A row move changes nothing so the property holds.
            A column move has the effect $inv + 3$ or $inv - 3$ for number of inversions $inv$
            and moves the blank square from row $i$ to either $i + 1$ or $i - 1$.
            
            The parity of both $i$ and $inv$ are changed.

            Since the parity was different from $m_{1} \cdots m_{n}$ it will stay different on $m_{n + 1}$.
            $P(n + 1)$ holds.
        \end{proof}
        \item
        \begin{proof}
            By Induction:
            $P(n)$ be the proposition that after $n$ steps the parity of
            number of inversions is odd.

            Base Case: For $n=0$. $P(0)$ is true. Since, we begin with odd parity and do nothing.

            Inductive Step: Assume it is true for all $n$. To show $P(n) \implies P(n + 1)$
            Consider a sequence of $n + 1$ moves, $m_{1}, m_{2}, \cdots m_{n + 1}$.

            Now by the inductive hypothesis, we know that
            after $m_{1} \cdots m_{n}$ is odd.

            Now, we know the parity of number of inversions does not change during
            $m_{n + 1}$. This implies that parity after $m_{1}, m_{2}, \cdots m_{n + 1}$
            is still odd. Thus, $P(n + 1)$ holds.
        \end{proof}

    }
\end{solution}


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
